Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
Remove paragraph about "theorems for free"
automatic -> automated + add a TBD

When wading through the numerous libraries written by
the Haskell community, one sometimes gets the impression that the type
system is being too much relied on, at the expense of testing.
While the type system cannot always guarantee semantic correctness,
test code has more applications than getting the code correct.
Test code assists developers in maintaining correctness when extending
software, and shows users how an API is supposed to be used.
To ease the production and enhance the value of test code, we advocate
behavior driven development with two tools:
QuickCheck integrated in Doctest for user documentation and Hspec
with new mnemonic combinators for code documentation.
Our method utilizes specification that can also be used for
documentation and automatic testing. We hope that this three-in-one
quality motivates Haskellers to write more test code.

@@

We agree that a function's type can reveal something about a
function's behavior~\cite{free}, but
there are many functions whose behavior cannot be guessed from their names and
type signatures.  One example is \verb|nub :: [a] -> [a]| from {\tt Data.List}.

@@

BDD includes TDD, amongst other software development methodologies,
but with a terminology and mindset shifted towards
specification instead of testing.
In BDD, specifications can be used for
automatic testing.
BDD is meant to be an enjoyable experience for the developer.
Compared to TDD it provides a much nicer syntax that
makes tests very easy to read.  And like TDD it puts emphasis on
test automation, to take work load from the shoulders of
developers.
BDD-style TDD has been pioneered by
RSpec~\cite{rspec}.  In this paper, we explore how to apply the TDD
aspect of BDD to Haskell.

@@

\noindent Our BDD procedure
can be used for design, documentation and automatic testing.
We hope that this kill-three-birds-with-one-stone aspect
motivates Haskellers to write test code.

@@

@@

\item It is important that testing is automated, including running of test
    suites.  Where should we put this?
\end{itemize}

>>>>

When wading through the numerous libraries written by
the Haskell community, one sometimes gets the impression that the type
system is being too much relied on, at the expense of testing.
While the type system cannot always guarantee semantic correctness,
test code has more applications than getting the code correct.
Test code assists developers in maintaining correctness when extending
software, and shows users how an API is supposed to be used.
To ease the production and enhance the value of test code, we advocate
behavior driven development with two tools:
QuickCheck integrated in Doctest for user documentation and Hspec
with new mnemonic combinators for code documentation.
Our method utilizes specification that can also be used for
documentation and automated testing. We hope that this three-in-one
quality motivates Haskellers to write more test code.

@@

@@

BDD includes TDD, amongst other software development methodologies,
but with a terminology and mindset shifted towards
specification instead of testing.
In BDD, specifications can be used for
automated testing.
BDD is meant to be an enjoyable experience for the developer.
Compared to TDD it provides a much nicer syntax that
makes tests very easy to read.  And like TDD it puts emphasis on
test automation, to take work load from the shoulders of
developers.
BDD-style TDD has been pioneered by
RSpec~\cite{rspec}.  In this paper, we explore how to apply the TDD
aspect of BDD to Haskell.

@@

\noindent Our BDD procedure
can be used for design, documentation and automated testing.
We hope that this kill-three-birds-with-one-stone aspect
motivates Haskellers to write test code.

@@

\begin{quote}
    TBD

@@

\item It is important that testing is automated, including running of test
    suites.  Where should we put this?

\item automatically sounds strange, better use automated somehow
\end{itemize}
\end{quote}
